---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# fastMN

<!-- badges: start -->
  [![R-CMD-check](https://github.com/ziyuliu1999/fastMN/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ziyuliu1999/fastMN/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->
  
The goal of fastMN is to efficiently compute the PDF and CDF of the matrix normal distribution and to rapidly generate random samples from it.

## Installation

You can install the development version of fastMN from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ziyuliu1999/fastMN")
```

## Functions

Three main functions introduced in the fastMN package

`fast_rmatnorm`: Sample random variables following matrix normal distributions

`fast_dmatnorm`: Calculate PDF of the matrix normal distribution

`fast_pnormmat`: Calculate CDF of the matrix normal distribution

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fastMN)
set.seed(1)

```

