---
title: "fastMN_vignettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fastMN_vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fastMN)
```


# Introduction
The matrix normal distribution is widely used in multivariate statistics for modeling data with matrix structures. The main advantage is the ability to model dependencies separately in rows and columns using covariance matrices and preserve the spatial structure in the analysis.

# Examples

## simple example
```{r}
set.seed(123)
# Define parameters
n <- 5
p <- 3
Z <- matrix(rnorm(n * p), nrow = n, ncol = p) # Random matrix
M <- matrix(0, nrow = n, ncol = p) # Mean matrix
U_cov <- diag(n) # Row covariance (identity)
V_cov <- diag(p) # Column covariance (identity)
Lower <- matrix(-3, nrow = n, ncol = p)  # Lower bound
Upper <- matrix(3, nrow = n, ncol = p)   # Upper bound
```

```{r}
samples <- fast_rmatnorm(n = n, p = p, M = M, U_cov = U_cov, V_cov = V_cov)
samples
```

```{r}
pdf <- fast_dmatnorm(Z, M, U_cov, V_cov)
pdf
```

```{r}
cdf <- fast_pnormmat(Lower, Upper, M, U_cov, V_cov, method = "pmvnorm")
cdf
```


## non-identity covariance matrix example
```{r}
set.seed(123)
n <- 10
p <- 5
M <- matrix(rnorm(n * p, mean = 1, sd = 2), nrow = n, ncol = p)
random_matrixU <- matrix(rnorm(n^2, mean = 0.3, sd = 0.5), nrow = n, ncol = n)
random_matrixV <- matrix(rnorm(p^2, mean = -0.1, sd = 0.4), nrow = p, ncol = p)
U_cov = crossprod(random_matrixU)
V_cov = crossprod(random_matrixV)
Lower <- matrix(-10, nrow = n, ncol = p)  # Lower bound
Upper <- matrix(10, nrow = n, ncol = p)   # Upper bound

samples <- fast_rmatnorm(n = n, p = p, M = M, U_cov = U_cov, V_cov = V_cov)
samples
pdf <- fast_dmatnorm(samples, M, U_cov, V_cov)
pdf

# cdf
fast_pnormmat(
  Lower = Lower, 
  Upper = Upper, 
  M = M, 
  U_cov = U_cov, 
  V_cov = V_cov, 
  method = "pmvnorm"
)
fast_pnormmat(
  Lower = Lower, 
  Upper = Upper, 
  M = M, 
  U_cov = U_cov, 
  V_cov = V_cov, 
  method = "sobol"
)
fast_pnormmat(
  Lower = Lower, 
  Upper = Upper, 
  M = M, 
  U_cov = U_cov, 
  V_cov = V_cov, 
  method = "naive_monte_carlo"
)
```

## performance check 
```{r, warning=FALSE}
microbenchmark::microbenchmark(
  fast_pnormmat(
    Lower = Lower, 
    Upper = Upper, 
    M = M, 
    U_cov = U_cov, 
    V_cov = V_cov, 
    method = "sobol",
    N = 10000
  ),
  fast_pnormmat(
    Lower = Lower, 
    Upper = Upper, 
    M = M, 
    U_cov = U_cov, 
    V_cov = V_cov, 
    method = "pmvnorm"
  ),
  fast_pnormmat(
    Lower = Lower, 
    Upper = Upper, 
    M = M, 
    U_cov = U_cov, 
    V_cov = V_cov, 
    method = "naive_monte_carlo",
    N = 10000
  ),
  times = 10)
```
